Methods for Polyphonic Music Transcription

### 2013-12-11 paper/paper.tex
added svm section
Added some parts to the paper

\citet{poliner2006discriminative}

% use support vector machines to predict note presence or absence at 10ms time steps based on

% one vs all
% frequency partition

@@

One of the great side-effects of NMF is that it often produces a sparse, parts-based representation. This is desirable in music transcription because the piano roll matrix, $H$, is a sparse matrix of note activations. However, the NMF method does not contain an explicit sparsity objective, and so the update rules do not always converge to a sparse solution. \citet{hoyer2004non} extended NMF to contain a tunable sparsity objective. This sparse NMF method in \citet{hoyer2004non} was adopted by \citet{abdallah2004polyphonic} in their transcription system.

% Non-negative Matrix factorization

@@

@@

\subsubsection{Reported measures}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 67.7\% & NR \\ \hline
SVM with HMM & 70\% & 34.2 \\ \hline
NMF & 23\% & 23 \\ \hline
Sparse NMF & 24\% & 24 \\ \hline
AdaBoost & 25\% & 25 \\ \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 51.7\% & 84.7  \\ \hline
SVM with HMM & 62.7\% & 53.8  \\ \hline
NMF & 20\% & 20 \\ \hline
Sparse NMF & 21\% & 21 \\ \hline
AdaBoost & 22\% & 22 \\ \hline
\end{tabular}
\end{center}

>>>>

% use support vector machines to predict note presence or absence at 10ms time steps based on
\citet{poliner2006discriminative} first used short-time Fourier transforms were applied to the audio data.  Then,  87(they omit the highest note) one-versus-all (OVA) SVM classifiers were trained, one for each note.  The SVM's were then used to predict the test data, and HMM's were used for post-process smoothing.
% one vs all
% frequency partition

@@

One of the great side-effects of NMF is that it often produces a sparse, parts-based representation. This is desirable in music transcription because the piano roll matrix, $H$, is a sparse matrix of note activations. However, the NMF method does not contain an explicit sparsity objective, and so the update rules do not always converge to a sparse solution. \citet{hoyer2004non} extended NMF to contain a tunable sparsity objective. This sparse NMF method in \citet{hoyer2004non} was adopted by \citet{abdallah2004polyphonic} in their transcription system.
% Non-negative Matrix factorization

@@

% \subsubsection{Median filtering}

@@

\subsubsection{Reported measures}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 67.7\% & - \\ \hline
SVM with HMM & 70\% & 34.2 \\ \hline
Sup. NMF & - & - \\ \hline
AdaBoost & 75.2\% & - \\ \hline
\end{tabular}
\end{center}
% precision, recall, f
% 42.3, 68.8, .524

@@

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 51.7\% & 84.7  \\ \hline
SVM with HMM & 62.7\% & 53.8  \\ \hline
Sup. NMF & 30.4\% & 92.4 \\ \hline
AdaBoost & 42.5\% & 113.9 \\ \hline
\end{tabular}
\end{center}
